\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
up to page 22 of minor edits

\begin{abstract}
Kinkaku-ji, the Temple of the Golden Pavilion, is one of Kyoto's most visited
tourist attractions. Most people who visit the site do not have the opportunity
to experience the rich art and culture that are part of its history. We worked
with our sponsor, Kyoto VR, to create an app that would allow visitors of 
Kinkaku-ji to better experience these aspects of the site. We used Unity to
create an audio tour app that provides historical insight on the location, 
displays galleries of art throughout the visit, and offers accessibility 
features through AR. We hope our app will enhance the experience of visiting
Kinkaku-ji.  
\end{abstract}

@@

We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto~VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer, as well as providing help with testing.
Further, we are grateful to the assistance and resources provided by Ritsumeikan
University and Professor Noma Haruo. Finally, a thank you to our advisers,
Professors Joshua Cuneo and Ralph Sutter. Without their expert advice and
feedback this project probably could not have been completed.

@@

Since our app had to deliver an audio tour supplemented by images based on your
latitude and longitude, we developed an internal tool to design physical
regions for each step of the tour. This tool, called Editour, provides a rich
editing suite through a simple web interface. Section~\ref{sec:editingATour}
goes into detail about the features of this web app. We also wrote a backend to
manage the tour files, allowing one of us (or our sponsor, Atticus Sims) to
download a zip file containing all of the media and info to reconstruct the
tour. This zip can be extracted into the source files for ARuko, which rebuilds
the tour from the downloaded contents. We were able to host the backend on the
server provided by Kyoto~VR's hosting plan; we discuss the hurdles that we
overcame to deploy the Editour backend with Kyoto~VR's current setup in
Section~\ref{sec:deployingTheEditourBackend}.

@@

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. Many AR apps require specific markers, like the those shown in
Figure~\ref{fig:arMarker}. Too avoid needing to place any physical object that
would disturb the buildings or grounds of a historic site our app does not rely
on these markers. Instead, ARuko recognizes images of objects that are already
at the site, and uses them to display informative AR pop-ups. See
Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
details.

@@

As smartphones and mobile technology become more prevalent, new forms of
human-computer interaction are becoming mainstream. Smartphones allow for an
unprecedented degree of connectivity with the digital world, but can also serve
as a tool for digitally enhancing the physical world. In this section we explain
the origins and uses of some of this technology.

@@

For example, AR can be used to display information about historical events,
places, and objects overlaid onto images of the real
world~\autocite{saenz2009}, in a way that is more intuitive or visually
appealing than a purely virtual environment. This provides the user with useful
information without needing to alter a real historic site.

@@

Even though it is still a developing technology, AR has been used in many
disparate disciplines, including data visualization~\autocite{resnick2017},
commerce~\autocite{matney2018}, marketing~\autocite{sharma2015},
education~\autocite{stewart-smith2012}, visual art~\autocite{katz2018}, and
even archaeology~\autocite{eve2012}.

@@

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they
primarily revolve around deploying gimmicks~\autocite{theappsolutions2018}. For
example, one of the most popular apps to use AR, \textit{Pokémon Go}, primarily
uses its AR feature to place a Pokémon on top of a camera's video feed.
Disappointingly, it does not interact with anything around it. It just floats a
fixed distance away from the user.

@@

AR apps are most commonly designed for smartphones due to their relatively low
cost and how accessible they are. However, smartphones come with a host of
hardware limitations that make achieving satisfying AR capabilities difficult.
Additionally, AR apps for smartphones tend not to be very user-friendly, and
oftentimes even complicate the task or activity they were meant to
enhance~\autocite{theappsolutions2018}.  The alternative then is to turn to
dedicated hardware, like Microsoft's HoloLens. The issue is that dedicated
hardware like the HoloLens is very inaccessible and expensive; Microsoft only
offers developer editions of the HoloLens, and for the incredibly steep price
of \$3,500~\autocite{microsoft2019}.

The challenges we faced during development mirrored those that plague the
industry as a whole very accurately. We struggled with how exactly we would use
AR for our app in a way that benefited the experience as a whole. Despite our
initial apprehension, we believe the way we have integrated AR into our app
enhances the user experience. Hardware issues were definitely our biggest
challenge. Only one member of our team had a phone new enough to run AR
technology at a decent level, making testing of our application difficult.

@@

Before our project started, Kyoto~VR was already using an app to deliver audio
tours. The app, called izi.TRAVEL, allows users to create audio tours with
audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel} but can be used for tours
of historic sites too. Kyoto~VR used the platform to make a simple audio tour
of Kinkaku-ji.

@@

Before we could start working on creating our app, we first needed to decide
which AR development platform to use. Based on our preliminary research, we
learned there are many powerful platforms available. There were many things we
needed to consider before deciding on a platform. These considerations included
what features the platform offered, which devices and operating systems the app
could run on, and the cost. Detailed below are some of the different platforms
we considered.

@@

Wikitude is another major AR development kit that is very prevalent in the
world of AR development. It has over 130,000 registered AR developers, and is
powering over 30,000 AR apps across smartphones, tablets, and smart
glasses~\autocite{wikitude2018}. It is easy to understand why Wikitude has so
many registered developers considering the list of features the platform
offers. Some of the features that appealed most to us were their ``Instant
Tracking,'' allowing for augmentation using flat surfaces; ``Image Tracking,''
allowing for augmentation using one or multiple 2D images; and ``Geo AR,''
allowing for creation of geo-markers at specific locations to trigger AR
content.

Wikitude supports Android, Apple, and Windows phones and tablets, as well as
smart glasses like the Epson Moverio, Microsoft HoloLens, and Vuzix smart
glasses. Additionally, many different development frameworks are capable of
running Wikitude's software development kit (SDK). According to Wikitude's
website, their SDK works with Windows, Android, and iOS development frameworks,
as well as ARCore and ARKit, Flutter, Cordova, Xamarin, and even Unity.

@@

Viro AR comes in two versions: ViroReact and ViroCore\autocite{facebook2019}.
ViroCore allows developers to build an AR Application with Java. The
disadvantage of this is that ViroCore only allows developers to target Android,
which unfortunately made ViroCore not an option for our project. ViroReact is
the cross-platform option for ViroAR. ViroReact leverages the cross-platform
capabilities of React, which is Facebook's JavaScript Library for developing
user interfaces~\autocite{facebook2019}.

@@

An alternative to building an app for a physical phone is to run it through an
emulator on a computer.

According to Techopedia, ``Emulation is the process of imitating a
hardware/software program/platform on another program or platform. This makes
it possible to run programs on systems not designed for
them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
up development. Loading programs onto the Android emulator is usually much
faster than installing an Android package file (APK) onto the actual device.
Additionally, emulators can mock almost all of the important features of an
actual Android device, including calls, text, GPS position, device rotation and
more~\autocite{androidemulator}.

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware. Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware~\autocite{alzaylaee2017}.
Conversely, errors that exist in the hardware version may not appear in the
emulation. Secondly, and most importantly for AR, it is common for emulation to
be much slower compared to real hardware.

In a question submitted to \textit{Compute!} magazine asking whether it is
possible for a Commodore 64 to emulate MS-DOS, the editor responded ``Yes, it's
possible for a 64 to emulate an IBM PC, in the same sense that it's possible to
bail out Lake Michigan with a teaspoon.'' The editor goes on to explain
``Emulation is a complex business, but here's one rule of thumb: The only way
to successfully emulate a machine is with a much more powerful
machine''~\autocite{warick1988}. In our case, emulating Android on a desktop
operating system is closer to emulating a C64 on an IBM PC running MS-DOS
(rather than the other way around, thankfully). The takeaway is that the speed
problem facing emulators is just as real as it was in 1988. Considering that AR
already pushes modern phone hardware to the limit, emulation is not something we
wanted to struggle with. On top of this, our testing required us to move the
camera through the world at various speeds and angles, which is simply
cumbersome with a laptop webcam.

As an alternative to emulation, ViroReact offers a convenient ``test bed'' for
rapidly testing your ViroReact app on native hardware without the need for an
emulator. This allowed us to get a real AR app up and running on our devices
much more easily than any of the other frameworks/engines we explored.
Unfortunately, the test bed app was somewhat unreliable based on our
experience; the test bed would frequently crash or would not be able to
download the files from the server. The most reliable way to test our app was
to compile a binary and manually install it onto our devices, which completely
defeated the purpose of the test bed app.

@@

Unity is a game engine that was originally introduced in
2005~\autocite{axon2016}. Because of the low barrier to entry---knowledge-wise
and price-wise---the engine quickly became incredibly popular. Ironically,
because the engine is so accessible that, Unity has faced a degree of critism.
Because Unity appeals to so many beginners, there are many unpolished games that
bear the Unity logo. In response to this sentiment, Marcos Sanchez, head of
global communications at Unity, "Democratizing development---in our minds, we
don't think is the wrong thing, we think it's the right thing. You want more
people understanding, and everyone’s gotta start somewhere"~\autocite{axon2016}.
Unity CEO John Riccitiello made the claim at TechCrunch Disrupt San Francisco
that half of all games are made with Unity \autocite{dillet2018}. We consider
Unity's ubiquity to be an advantage; there is a glut of information about how to
use augmented reality within Unity.

@@

All of Unity's scripting is done with C\#, which is a general purpose,
object-oriented language~\autocite{ecmainternational2017}. Even though none of
us had extensive experience with C\# prior to this project, this was not a great
concern since C\# is similar to other object-oriented languages such as Java and
C++. The design goals of the language were also appealing to us; C\# includes
features important for programmer productivity such as strong type checking
(unlike JavaScript), detection of using uninitialized variables (also unlike
JavaScript,) range checking for array bounds (unlike C) and garbage collection.
At the same time, our lack of familiarity with the language and Unity as a whole
is another reason we first looked into cross-platform AR solutions that did not
use Unity.
%TODO see if we need more sources for this

@@

In this section we discuss and implementation of ARuko and Editour, including
the technologies and techniques involved in creating both of them. We also
discuss the design decisions we made and some of the challenges we faced in
creating these applications.

@@

The first subcard seen in Figure~\ref{fig:renameSubcard} is the ``Rename''
subcard, which is fairly self-explanatory.  This section expands to reveal a
textbox, allowing the user to rename the region after clicking ``Okay'' or
hitting the enter key.\footnote{There are multiple places in the UI where a
textbox is immediately adjacent to a ``Confirm'' button.  We made sure all of
these can be triggered by simply hitting enter, since this is common behavior
when filling out forms on the web.}

@@

The second subcard seen in Figure~\ref{fig:mediaSubcard} is slightly more
involved. Expanding the ``Media'' subcard by clicking on the green bar will
reveal a bevy of options for augmenting the audio, images, and text to be
associated with that region of the tour. From here, the user can upload an
audio file and multiple image files from his or her hard drive with the two
file-select fields. If the user is editing an existing tour that has already
been uploaded, the names of the files already present on the server will appear
as cards with `X' buttons. This allows the user to remove images or audio from
that region even after the tour has been uploaded.

@@

The third subcard is the ``Points'' subcard. This subcard can be revealed in
one of two ways. The first way is by clicking on the yellow bar labeled
``Points'', which is the same for all subcards. Alternatively, the user can
click directly on the region on the map. The region will flash yellow and be
scrolled into view to let the user know which region was clicked on. Both of
these methods will enable editing mode, whereby the user can directly
manipulate the vertices that make up the region. Blue circles appear on top of
each vertex, and red circles appear at the midpoint of each edge. Clicking on a
red midpoint will add an additional vertex at that midpoint. Dragging one of
the blue vertices will move the vertex around. The latitude and longitude are
updated in the ``Points'' subcard as the user drags the vertex around. Clicking
on the vertex directly will create a blue pin-shaped marker that the user can
also drag. Clicking on the coordinate box in the subcard will also create this
blue pin-shaped marker; the map will also pan to this coordinate. The user can
also delete vertices in the same way that files can be deleted from the
``Media'' subcard by clicking on the `X' button on that vertex's coordinate
card. If there are exactly three points in a region, the `X' buttons will be
``grayed-out,'' preventing the user from deleting any more points, since a
polygon must consist of at least three points.

@@

The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
subcard. When revealed, another button will appear labeled ``Really Delete.''
The action can be canceled by collapsing the subcard by hitting the bar now
labeled ``Don't Delete!'' This prevents the user from accidentally deleting a
region he or she did not mean to remove.

@@

%update this figure
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{editour.jpg}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

@@

The frontend was implemented as a web application, using web technologies such
as HTML, CSS and JavaScript, with JavaScript being the vast majority of the
code. Type-checking provided by Visual Studio Code and JSDoc made the growing
code complexity more manageable.\footnote{One helpful specification of the
ECMAScript standard in the way of programmer sanity is ``strict mode.'' By
placing the string \texttt{"use strict"} at the top of a JavaScript source file,
errors will be thrown in many cases where ordinary JavaScript would not
complain. The simplest example of this is the line \texttt{a = 1;} will not
throw an error ordinarily. In strict mode, you must at first explicitly declare
the variable with the \texttt{let}, \texttt{var}, or \texttt{const} keyword
before assigning it, similar to Java or C++. We included the string at the
beginning of every source file except for class declarations, which are in
strict mode by default~\autocite[386]{ecmainternational2019}.} Excluding Node.js
modules, the only external library we used for Editour was Leaflet, which is
``an open-source JavaScript library for mobile-friendly interactive maps''
according to the official Leaflet website~\autocite{leafletjs}. We did not use
any framework for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel. For
a JavaScript project of this scope, this was the correct decision. Considering
we had limited knowledge of React or Angular, it was also faster to develop the
UI in the way we were used to from previous experience. But if we were to
continue to develop Editour, UI libraries and frontend build tools would be
something to consider.

@@

The backend implements a representational state transfer (REST) API.
In a ``RESTful'' service, web resources are manipulated with a predefined set of
stateless operations~\autocite{rfc7231}. Because the REST API is operated over
the Hypertext Transfer Protocol (HTTP), the available operations are just the
standard HTTP methods, such as GET, POST, and DELETE. For full documentation of
the backend's API, see Appendix~\ref{sec:editourAPIDocumentation}.

@@

The files produced by Editour could be used to power an app that does not
incorporate AR, such as an audio guide mobile web app that runs entirely in the
browser, using the geolocation API to access the user's location (if the user
grants permission.) This kind of infrastructure would allow users to access an
audio tour---supplemented by images and audio transcripts---without the need to
download an app at all. By simply visiting a link, a user could experience a
guided tour that changes as the user walks through the route. For example,
colleges could distribute tour links via QR codes, which would instantly launch
an interactive guided tour of the campus through the browser.

Currently, anyone can clone the GitHub repository of Editour and deploy a
working version on a personal server. The source code for Editour is under a
free license. This allows anyone to expand the frontend and backend to suit
their needs. With additional hardware and by extending the current
implementation of both the frontend and backend, Editour could be used as the
groundwork to create an entire crowd-sourced walking tour platform, allowing
users to design tours for others to take.

@@

ARuko uses augmented reality to translate text at the site as well. While AR
translation apps exist, the experience can be frustrating, and produce poor
results. Google's text recognition and machine-learning powered translation
technology is certainly impressive. At the same time, the translation service
works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
the app attempts to translate text as quickly as possible, superimposing the
translated text onto the real world using the camera. %could put an image of instant mode here as an example
In ``scan'' mode, the user first takes a photo. Then, the user is prompted to 
highlight where text appears in the photo. %could put an example here as well
After the translation is complete, the translated text appears in a separate UI %another example?
element instead superimposed onto the photo. In most cases, it is more 
convenient and readable to have the translation appear in a separate scrollable
text box. This motivated the current design of the ``info buttons'' in ARuko. 
Instead of placing text directly onto signage, we place a blue button with a 
stylized `i' in the center. By tapping on this button, a separate UI element 
will appear containing the translated text. Since this button is cast into the %example
world using the AR camera, the button appears to be placed directly onto the 
content in the real world.

>>>>

\begin{abstract}
Kinkaku-ji, the Temple of the Golden Pavilion, is one of Kyoto's most visited
tourist attractions. Most people who visit the site do not have the opportunity
to experience the rich art and culture that are part of its history. We worked
with our sponsor, Kyoto VR, to create an app that would allow visitors of
Kinkaku-ji to better experience these aspects of the site. We used Unity to
create an audio tour app that provides historical insight on the location,
displays galleries of art throughout the visit, and offers accessibility
features through AR. We also developed a tool to aid in the design and creation
of audio tours. We hope our app will enhance the experience of visiting
Kinkaku-ji.  
\end{abstract}

@@

% TODO is starting with "A special thank you" a complete clause?
We would also like to thank Inoue Hikaru for his help with translations and
researching AR technology. A special thank you to the IQP team working with
Kyoto~VR, Lewis Cook, Nicole Escobar, Ahad Fareed, and Cameron Person, for
filming and editing the app trailer, as well as providing help with testing.
Further, we are grateful to the assistance and resources provided by Ritsumeikan
University and Professor Noma Haruo. Finally, a thank you to our advisers,
Professors Joshua Cuneo and Ralph Sutter. Without their expert advice and
feedback this project probably could not have been completed.

@@

Since our app had to deliver an audio tour supplemented by images based on the
user's latitude and longitude, we developed an internal tool to design physical
regions for each step of the tour. This tool, called Editour, provides a rich
editing suite through a simple web interface. Section~\ref{sec:editingATour}
goes into detail about the features of this web app. We also wrote a backend to
manage the tour files, allowing one of us (or our sponsor, Atticus Sims) to
download a zip file containing all of the media and info to reconstruct the
tour. This zip can be extracted into the source files for ARuko, which rebuilds
the tour from the downloaded contents. We were able to host the backend on the
server provided by Kyoto~VR's hosting plan; we discuss the hurdles that we
overcame to deploy the Editour backend with Kyoto~VR's current setup in
Section~\ref{sec:deployingTheEditourBackend}.

@@

To solve this problem and open up the peerless beauty of the Golden Pavilion to
more people, our team created ARuko and Editour. These two tools comprise a
complete platform for designing and experiencing AR-enhanced tours. Editour
makes it easy to design custom audio tours including audio, text, and images,
while ARuko allows users to seamlessly experience historic sites in an intuitive
and novel way. Many AR apps require specific markers, like the those shown in
Figure~\ref{fig:arMarker}. To avoid the need to place any physical object that
would disturb the buildings or grounds of a historic site, our app does not rely
on these markers. Instead, ARuko recognizes images of objects that are already
at the site, and uses them to display informative AR pop-ups. See
Sections~\ref{sec:translationFeature} and \ref{sec:mapOverlayFeature} for more
details.

@@

As smartphones and mobile technology become more prevalent, new forms of
human-computer interaction are becoming mainstream. Smartphones allow for an
unprecedented degree of connectivity with the digital world, but can also serve
as a tool for digitally enhancing the physical world. In this section we explain
the origins and uses of this technology.

@@

For example, AR can be used to display information about historical events,
places, and objects overlaid onto images of the real
world~\autocite{saenz2009}, in a way that is more intuitive or visually
appealing than a purely virtual environment. This provides the user with useful
information without needing to alter the physical historic site.

@@

Even though AR is still a developing technology, it has been used in many
disparate disciplines, including data visualization~\autocite{resnick2017},
commerce~\autocite{matney2018}, marketing~\autocite{sharma2015},
education~\autocite{stewart-smith2012}, visual art~\autocite{katz2018}, and
even archaeology~\autocite{eve2012}.

@@

Many of the applications and use cases that exist for AR right now are, simply
put, not very good. Many AR apps and features available on smartphones offer
very little in the way of functionality or practicality; quite simply, they
primarily revolve around deploying gimmicks~\autocite{theappsolutions2018}. For
example, one of the most popular apps to use AR, \textit{Pokémon Go}, primarily
uses its AR feature to place a Pokémon on top of a camera's video feed.
Disappointingly, the Pokémon does not interact with anything around it. It just
floats a fixed distance away from the user.

@@

AR apps are most commonly designed for smartphones due to their relatively low
cost and how accessible they are. However, smartphones come with a host of
hardware limitations that make achieving satisfying AR capabilities difficult.
Additionally, AR apps for smartphones tend not to be very user-friendly, and
oftentimes even complicate the task or activity they were meant to
enhance~\autocite{theappsolutions2018}.  The alternative then is to turn to
dedicated hardware, like Microsoft's HoloLens. The issue is that dedicated
hardware like the HoloLens is very inaccessible and expensive; Microsoft only
offers developer editions of the HoloLens, and for the steep price of
\$3,500~\autocite{microsoft2019}.

The challenges we faced during development mirrored those that plague the
industry as a whole very accurately. We struggled with how exactly we would use
AR for our app in a way that benefited the experience as a whole. Despite our
initial apprehension, we believe the way we have integrated AR into our app
enhances the user experience. One of our largest challenges came from the lack
of hardware on which to test. Only one member of our team had a phone new enough
to run AR technology at a decent level, making testing of our application
difficult.

@@

Before our project had begun, Kyoto~VR was already using an app to deliver audio
tours. The app, called izi.TRAVEL, allows users to create audio tours with
audio and image files tied to specific locations in the real
world~\autocite{izitravel2015} (see Figure \ref{fig:iziTravel}). The app is
aimed at museums and city tours~\autocite{izitravel} but can be used for tours
of historic sites too. Kyoto~VR used the platform to make a simple audio tour
of Kinkaku-ji.

@@

Before we could start working on creating our app, we first needed to decide
which AR development platform to use. Based on our preliminary research, we
learned there are many powerful platforms available. There were many things we
needed to consider before deciding on a platform---considerations such as what
features the platform offered, which devices and operating systems the app could
run on, and the cost. Detailed below are some of the different platforms and
technologies we considered.

@@

Wikitude is another major AR development kit that is very prevalent in the
world of AR development. It has over 130,000 registered AR developers, and is
powering over 30,000 AR apps across smartphones, tablets, and smart
glasses~\autocite{wikitude2018}. It is easy to understand why Wikitude has so
many registered developers considering the list of features the platform
offers. Some of the features that most appealing to us were their ``Instant
Tracking,'' allowing for augmentation using flat surfaces; ``Image Tracking,''
allowing for augmentation using one or multiple 2D images; and ``Geo AR,''
allowing for creation of geo-markers at specific locations to trigger AR
content.

Wikitude supports Android, Apple, and Windows phones and tablets, as well as
smart glasses like the Epson Moverio, Microsoft HoloLens, and Vuzix smart
glasses. Additionally, many different development frameworks are capable of
running Wikitude's software development kit (SDK). According to Wikitude's
website, their SDK works with Windows, Android, and iOS development frameworks,
as well as ARCore and ARKit, Flutter, Cordova, Xamarin, and Unity.

@@

Viro AR comes in two versions: ViroReact and ViroCore~\autocite{viro2019}.
ViroCore allows developers to build an AR Application with Java. The
disadvantage of this is that ViroCore only allows developers to target Android,
which unfortunately made ViroCore not an option for our project; one of the
requirements from our sponsor was that the app had to be cross-platform.
ViroReact is the cross-platform option for ViroAR. ViroReact leverages the
cross-platform capabilities of React, which is Facebook's JavaScript Library for
developing user interfaces~\autocite{facebook2019}.

@@

An alternative to building an app for a physical phone is to run it through an
emulator on a computer. According to Techopedia, ``Emulation is the process of
imitating a hardware/software program/platform on another program or platform.
This makes it possible to run programs on systems not designed for
them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
up development. Loading programs onto the Android emulator is usually much
faster than installing an Android package file (APK) onto the actual device.
Additionally, emulators can mock almost all of the important features of an
actual Android device, including calls, text, GPS position, device rotation and
more~\autocite{androidemulator}.

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware. Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware~\autocite{alzaylaee2017}.
Conversely, errors that exist in the hardware version may not appear in the
emulation. Secondly, and most importantly for AR, it is common for emulation to
be much slower compared to real hardware.\footnote{In a question submitted to
\textit{Compute!} magazine asking whether it is possible for a Commodore 64 to
emulate MS-DOS, the editor responded ``Yes, it's possible for a 64 to emulate an
IBM PC, in the same sense that it's possible to bail out Lake Michigan with a
teaspoon.'' The editor goes on to explain ``Emulation is a complex business, but
here's one rule of thumb: The only way to successfully emulate a machine is with
a much more powerful machine''~\autocite{warick1988}. In our case, emulating
Android on a desktop operating system is closer to emulating a C64 on an IBM PC
running MS-DOS (rather than the other way around, thankfully). The takeaway is
that the speed problem facing emulators is just as real as it was in 1988.}
Considering that AR already pushes modern phone hardware to the limit, emulation
is not something we wanted to struggle with. On top of this, our testing
required us to move the camera through the world at various speeds and angles,
which is simply cumbersome with a laptop webcam.

As an alternative to emulation or compiling a native binary, ViroReact offers a
convenient ``test bed'' for rapidly testing your ViroReact app on native
hardware without the need for an emulator. This allowed us to launch a working
AR app on our devices much more easily than any of the other frameworks or
engines we explored. Unfortunately, the test bed app was somewhat unreliable
based on our experience; the test bed would frequently crash or would not be
able to download the files from the server. The most reliable way to test our
app was to compile a binary and manually install it onto our devices, which
completely defeated the purpose of the test bed app.

@@

Unity is a game engine that was originally introduced in
2005~\autocite{axon2016}. Because of the low barrier to entry---experience-wise
and price-wise---the engine quickly became incredibly popular. Ironically,
because the engine is so accessible, Unity has faced a degree of critism.
Because Unity appeals to so many beginners, there are many unpolished games that
bear the Unity logo. In response to this sentiment, Marcos Sanchez, head of
global communications at Unity, said "Democratizing development---in our minds,
we don't think is the wrong thing, we think it's the right thing. You want more
people understanding, and everyone’s gotta start somewhere"~\autocite{axon2016}.
Unity CEO John Riccitiello made the claim at TechCrunch Disrupt San Francisco
that half of all games are made with Unity \autocite{dillet2018}. We consider
Unity's ubiquity to be an advantage; there is a glut of information about how to
use augmented reality within Unity.

@@

All of Unity's scripting is done with C\#, which is a general purpose,
object-oriented language~\autocite{ecmainternational2017}. Even though none of
us had extensive experience with C\# prior to this project, this was not of
great concern since C\# is similar to other object-oriented languages such as
Java and C++. The design goals of the language were also appealing to us; C\#
includes features important for programmer productivity such as strong type
checking (unlike JavaScript), detection of using uninitialized variables (also
unlike normal JavaScript,) range checking for array bounds (unlike C) and
garbage collection. At the same time, our lack of familiarity with the language
and Unity as a whole is another reason we first looked into cross-platform AR
solutions that did not use Unity.
%TODO see if we need more sources for this

@@

In this section we discuss the implementation of ARuko and Editour, which are
the names for the mobile AR mobile app and web-based tour editor respectively.
We also discuss the technologies and techniques involved in creating both of
them, along with the the design decisions we made and challenges we faced in
creating these applications.

@@

The first subcard seen in Figure~\ref{fig:renameSubcard} is the ``Rename''
subcard. This section expands to reveal a textbox, allowing the user to rename
the region after clicking ``Okay'' or hitting the enter key.\footnote{There are
multiple places in the UI where a textbox is immediately adjacent to a
``Confirm'' button.  We made sure all of these can be triggered by simply
hitting enter, since this is common behavior when filling out forms on the web.}

@@

The second subcard seen in Figure~\ref{fig:mediaSubcard} is more involved.
Expanding the ``Media'' subcard by clicking on the green bar will reveal a bevy
of options for augmenting the audio, images, and text to be associated with that
region of the tour. From here, the user can upload an audio file and multiple
image files from the user's hard drive with the two file-select fields. If the
user is editing an existing tour that has already been uploaded, the names of
the files already present on the server will appear as cards with `X' buttons.
This allows the user to remove images or audio from that region even after the
tour has been uploaded.

@@

The third subcard is the ``Points'' subcard. This subcard can be revealed in one
of two ways. The first way is by clicking on the yellow bar labeled ``Points'',
which is the same for all subcards. Alternatively, the user can click directly
on the region on the map. The region will flash yellow and be scrolled into view
to let the user know which region was clicked on. Both of these methods will
enable editing mode, whereby the user can directly manipulate the vertices that
make up the region. Blue circles appear on top of each vertex, and red circles
appear at the midpoint of each edge. Clicking on a red midpoint will add an
additional vertex at that midpoint. Dragging one of the blue vertices will move
the vertex around. The latitude and longitude are updated in the ``Points''
subcard as the user moves the vertex. Clicking on the vertex directly will
create a blue pin-shaped marker that the user can also drag. Clicking on the
coordinate box in the subcard will also create this blue pin-shaped marker; the
map will also pan to this coordinate. The user can also delete vertices in the
same way that files can be deleted from the ``Media'' subcard by clicking on the
`X' button on that vertex's coordinate card. If there are exactly three points
in a region, the `X' buttons will be ``grayed-out,'' preventing the user from
deleting any more points, since a polygon must consist of at least three points.

@@

The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
subcard. When revealed, another button will appear labeled ``Really Delete.''
The action can be canceled by collapsing the subcard by hitting the bar now
labeled ``Don't Delete!'' This prevents the user from accidentally deleting a
region unintentionally.

@@

% TODO update this figure
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{editour.jpg}
	\caption{A screenshot of the Editour web app frontend}
	\label{fig:editour}
\end{figure}

@@

The frontend was implemented as a web application, using web technologies such
as HTML, CSS and JavaScript, with JavaScript being the vast majority of the
code. Type-checking provided by Visual Studio Code and JSDoc made the growing
code complexity more manageable.\footnote{One helpful specification of the
ECMAScript standard in the way of programmer sanity is ``strict mode.'' By
placing the string \texttt{"use strict"} at the top of a JavaScript source file,
errors will be thrown in many cases where ordinary JavaScript would not
complain. The simplest example of this is the line \texttt{a = 1;} will not
throw an error ordinarily. In strict mode, you must at first explicitly declare
the variable with the \texttt{let}, \texttt{var}, or \texttt{const} keyword
before assigning it, similar to Java or C++. We included the string at the
beginning of every source file except for class declarations, which are in
strict mode by default~\autocite[386]{ecmainternational2019}.} Excluding Node.js
modules, the only external library we used for Editour was Leaflet, which is
``an open-source JavaScript library for mobile-friendly interactive maps''
according to the official Leaflet website~\autocite{leafletjs}. We did not use
any framework for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel. For
a JavaScript project of this scope, this was the correct decision. Considering
we had limited knowledge of React or Angular, it was also faster to develop the
UI in the way we were used to from previous experience, but if we were to
continue to develop Editour, UI libraries and frontend build tools would be
something to consider.

@@

% TODO explain what stateless operations are
The backend implements a representational state transfer (REST) API.
In a ``RESTful'' service, web resources are manipulated with a predefined set of
stateless operations~\autocite{rfc7231}. Because the REST API is operated over
the Hypertext Transfer Protocol (HTTP), the available operations are just the
standard HTTP methods, such as GET, POST, and DELETE. For full documentation of
the backend's API, see Appendix~\ref{sec:editourAPIDocumentation}.

@@

The files produced by Editour could be used to power an app that does not
incorporate AR, such as an audio guide mobile web app that runs entirely in the
browser, using the geolocation API to access the user's location (if the user
grants permission). This kind of infrastructure would allow users to access an
audio tour---supplemented by images and audio transcripts---without the need to
download an app at all. By simply visiting a link, a user could experience a
guided tour that changes as the user walks through the route. For example,
colleges could distribute tour links via QR codes, which would instantly launch
an interactive guided tour of the campus through the browser.

Currently, anyone can clone the GitHub repository of Editour and deploy a
working version on a personal server. The source code for Editour is under a
free license, namely the GNU General Public License. This allows anyone to
expand the frontend and backend to suit their needs. With additional hardware
and by extending the current implementation of both the frontend and backend,
Editour could be used as the groundwork to create an entire crowd-sourced
walking tour platform, allowing users to design tours for others to take.

@@

% TODO include photos of the google translation app including our own app
ARuko uses augmented reality to translate text at the site as well. While AR
translation apps exist, the experience can be frustrating, and produce poor
results. Google's text recognition and machine-learning powered translation
technology is certainly impressive. At the same time, the translation service
works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
the app attempts to translate text as quickly as possible, superimposing the
translated text onto the real world using the camera. In ``scan'' mode, the user
first takes a photo. Then, the user is prompted to highlight where text appears
in the photo. After the translation is complete, the translated text appears in
a separate UI element instead superimposed onto the photo. In most cases, it is
more convenient and readable to have the translation appear in a separate
scrollable text box. This motivated the current design of the ``info buttons''
in ARuko. Instead of placing text directly onto signage, we place a blue button
with a stylized `i' in the center. By tapping on this button, a separate UI
element will appear containing the translated text. Since this button is cast
into the world using the AR camera, the button appears to be placed directly
onto the content in the real world.
